# diverstidy 

<center>
[insert image here]
</center>

## Demographic Analysis  

### `detect_ancestry_terms()`

```{r, eval=FALSE}
detect_ancestry_terms(id, input)
```

### `detect_cultural_terms()`

```{r, eval=FALSE}
detect_cultural_terms(id, input)
```

### `detect_disability_terms()`

```{r, eval=FALSE}
detect_disability_terms(id, input)
```

### `detect_diversity_terms()`

```{r, eval=FALSE}
detect_diversity_terms(id, input)
```

### `detect_equity_terms()`

```{r, eval=FALSE}
detect_equity_terms(id, input)
```

### `detect_justice_terms()`

```{r, eval=FALSE}
detect_justice_terms(id, input)
```

### `detect_lifecourse_terms()`

```{r, eval=FALSE}
detect_lifecourse_terms(id, input)
```

### `detect_migration_terms()`

```{r, eval=FALSE}
detect_migration_terms(id, input)
```

### `detect_minority_terms()`

```{r, eval=FALSE}
detect_minority_terms(id, input)
```

### `detect_racialethnic_terms()`

```{r, eval=FALSE}
detect_racialethnic_terms(id, input)
```

### `detect_religious_terms()`

```{r, eval=FALSE}
detect_religious_terms(id, input)
```

### `detect_sexgender_terms()`

```{r, eval=FALSE}
detect_sexgender_terms(id, input)
```

### `detect_sexuality_terms()`

```{r, eval=FALSE}
detect_sexuality_terms(id, input)
```

### `detect_socialclass_terms()`

```{r, eval=FALSE}
detect_socialclass_terms(id, input)
```

## Geographic Analysis 

### `detect_countries()` 

Sources for output parameters:

1. `country`: Country names based on International Organization for Standardization with all punctuation removed to allow names to be more readable ([ISO](https://www.iso.org/obp/ui/#home)).
2. `iso_2`: International Organization for Standardization's two-digit country codes ([ISO](https://www.iso.org/obp/ui/#home)). NOTE: The [CIA World Factbook](https://www.cia.gov/the-world-factbook/references/country-data-codes/) uses a Geopolitical Entities and Codes (GEC) (Formerly FIPS 1PUB 10-4) schema that is now based on the ISO-2. 
3. `iso_3`: International Organization for Standardization's three-digit country codes ([ISO](https://www.iso.org/obp/ui/#home)). NOTE: The [CIA World Factbook](https://www.cia.gov/the-world-factbook/references/country-data-codes/) uses a Letter Codes for Geographical Entities Standardization Agreement (STANAG) that is based on the ISO-3. 
4. `iso_numeric`: International Organization for Standardization's three-digit numeric codes ([ISO](https://www.iso.org/obp/ui/#home)) NOTE: The [United Nations](https://unstats.un.org/unsd/methodology/m49/) also uses the ISO numeric code as their M49 area codes.
5. `iso_domain`: International Organization for Standardization's three-digit numeric codes ([ISO](https://www.iso.org/obp/ui/#home))
6. `continent`: Continents that each country is located based onon International Organization for Standardization ([ISO](https://www.iso.org/obp/ui/#home)).
7. `region`: Regions each country are in based on the [United Nations' M49 classification](https://unstats.un.org/unsd/methodology/m49/). 
8. `sub_region`: Subregions each country are in based on the [United Nations' M49 classification](https://unstats.un.org/unsd/methodology/m49/).
9. `int_region`: Intermediary regions each country are in based on the [United Nations' M49 classification](https://unstats.un.org/unsd/methodology/m49/).
10. `country_english`: Country names based verbatim on International Organization for Standardization ([ISO](https://www.iso.org/obp/ui/#home)).
11. `country_chinese`: Country names in Chinese as translated by the [United Nations](https://unstats.un.org/unsd/methodology/m49/).  
12. `country_russian`: Country names in Russian as translated by the [United Nations](https://unstats.un.org/unsd/methodology/m49/). 
13. `country_french`: Country names in French as translated by the [United Nations](https://unstats.un.org/unsd/methodology/m49/). 
14. `country_spanish`: Country names in Spanish as translated by the [United Nations](https://unstats.un.org/unsd/methodology/m49/). 
15. `country_arabic`: Country names in Arabic as translated by the [United Nations](https://unstats.un.org/unsd/methodology/m49/). 
16. `latitude` and `longitude`: Averaged latitude and longitude taken from [Gapminder](https://www.gapminder.org/data/geo/)

## Population Labeling 

### `detect_human_terms()`

```{r, eval=FALSE}
detect_human_terms(id, input)
```




